%-------------------------
% Resume in Latex
% Author : Haoyao Chen
% License : MIT
%------------------------ 
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy} 
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\bulletItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItem}[2]{
  \item[]\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProject}[2]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Haoyao Chen} &  \href{mailto:haoyao.chen.work@gmail.com}{haoyao.chen.work@gmail.com} $\vert$ (949) 293-2620 \\
  San Jose, CA & linkedin.com/in/hchencs\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Santa Clara University}{Santa Clara, CA}
      {Master of Science in Computer Science  GPA: 3.96/4.00}{Sep 2019 -- Mar 2021}
      \resumeSubheading
      {University of California, Davis}{Davis, CA}
      {Bachelor of Science in Computer Science  GPA: 3.22/4.00 (including transfer units)}{Oct 2014 -- Jun 2016}
  \resumeSubHeadingListEnd

% --------Relevant Courses------------
\section{Relevant Courses}
Data Structures and Algorithms, Operating Systems, Computer Architecture, Computer Networks, \\
Software Engineering, Database Systems, Distributed Systems, Cloud Computing, Parallel Programming, Machine Learning

% --------Technical Skillset------------
\section{Technical Skillset}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{Java, C, C++, Python, Scala, Javascript}
% \resumeSubItem{Other skills}{Unix/Linux, Git, Apache Spark, Apache Kafka, Hadoop, HDFS, SQL, NoSQL, MongoDB, MySQL, RESTful API, GraphQL, React, Angular JS, Jenkins, Maven, AWS (S3, EC2, CloudFormation, IAM, DynamoDB, RDS)}
\resumeSubItem{Other skills}{Unix/Linux, Git, Apache Spark, Apache Hive, Apache Kafka, SQL, NoSQL, MySQL, Apache, Tomcat, AWS (S3, EC2, CloudFormation, IAM, DynamoDB, RDS, EMR), HTML, CSS}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Amazon Web Services}{Santa Clara, CA}
    {Software Engineer Intern}{Jun 2020 - Sep 2020}
    \begin{itemize} 
      \bulletItem {Won a \textbf{full-time return offer} for recognition of my job performance and work ethics.}
      \bulletItem {Developed a highly demanded feature for a growing cloud database service with 2,000 customers and 3 billion requests per day. This feature provides a public API for customers to apply configurations, including connection limit, to their database instances.}
      \bulletItem {Created a thorough design for my project that includes user interface, architecture, data schema, and logic flow.}
      \bulletItem {Wrote code with attention to details and quality, maintaining pull request revisions to fewer than 3.}
      \bulletItem {Demonstrated ownership by driving the project from requirement definition to release in 10 weeks.}
      \bulletItem {Ensured timely delivery of my project through proactive communication with stakeholders inside and outside my organization.}
      \bulletItem {Raised the quality bar for my colleagues' work through design reviews and code reviews on a daily basis, going beyond the requirement for interns.}
      \bulletItem {Boosted morale for my team by organizing online and offline social activities while working remotely.}
    \end{itemize}

    \resumeSubheading
      {UiPath}{Tokyo, Japan}
      {Technical Consultant}{Oct 2018 - Aug 2019}
      \begin{itemize} 
        \bulletItem {Won company-wide \textit{Best Project Award} for successfully delivering a USD 6 million project. (Team size: 10)}
        \bulletItem {Established coding convention, version control, CI/CD for a development project with more 100 developers.}
        \bulletItem {Hosted weekly tech seminar introduce development best practices, helping more than 40 developers improve productivity and code quality.}
        \bulletItem {Discovered and reproduced 10 regressions of a major software version, contributing to its successful release.}
        \bulletItem {Coordinated product feature development by gathering customer feedback and communicating those feedback with development teams, increasing customer satisfaction and making UiPath competitive.}
      \end{itemize}

    \resumeSubheading
      {Rakuten}{Tokyo, Japan}
      {Software Engineer}{Oct 2016 - Sep 2018}
      \begin{itemize} 
        \bulletItem {Developed web applications for clients to purchase and manage Ad campaigns.}
        \bulletItem {Led effort to scale up a growing Ad business by migrating data pipelines to Apache Spark. Established best practice for Spark program design and performance tuning.}
        \bulletItem {Created business intelligence dashboards to visualize search trends and Ad sales opportunities, enabling business teams to prioritize Ad clients based on revenue potential.} 
        \bulletItem {Coordinated development projects between business development teams and software development teams to ensure that software products are developed to precise specification.}
        \bulletItem {Improved system stability and service quality by proactively fixing bugs in backlog.}
        \bulletItem {Mentored new graduates to help them become successful members of my organization.}
      \end{itemize}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
% \section{Projects}

%   \resumeSubHeadingListStart
%     \resumeProject{Cloud Database Granular Control (Amazon Web Services)}{Jun 2020 - Sep 2020}
%     \begin{itemize} 
%       \bulletItem{Built highly demanded feature for customers to apply scaling configurations to their cloud databases} 
%       \bulletItem{Created additional public APIs and backend logic for a rapidly growing service with 2,000 customers and 3 billion requests per day}
%       \bulletItem{Completed all stages of the project, from design to beta release, in 10 weeks}
%     \end{itemize}

%   \resumeProject{Data pipeline scale-up (Rakuten)}{Sep 2017 - Mar 2018}
%     \begin{itemize} 
%       \bulletItem{Led effort to scale-up Ad business's data pipeline using Apache Spark}
%       \bulletItem{Created new data pipelines that can efficiently process billions of lines of log data per day}
%     \end{itemize}
%   \resumeSubHeadingListEnd

\end{document}